Analyzing the Effect of Surface in Tennis Grand Slams

### 2018-09-07 contest/surface-type/paper-tennis.Rmd
kayla small edits; remove saveds

saveRDS(gs, "../../data/gs_2013_2017.rda")

@@

```{r data-cleaning, include = FALSE}
## Add new columns of winner points won, loser points won, and whether the winner had more points
gs <- gs %>% mutate(w_pointswon = w_1stWon + w_2ndWon + l_svpt - l_1stWon - l_2ndWon)
gs <- gs %>% mutate(l_pointswon = l_1stWon + l_2ndWon + w_svpt - w_1stWon - w_2ndWon)
gs <- gs %>% mutate(w_morepts = w_pointswon >= l_pointswon)

@@

>>>>

# saveRDS(gs, "../../data/gs_2013_2017.rda")

@@

```{r data-cleaning, include = FALSE}
## Add new columns of winner points won, loser points won, and whether the winner had more points
gs <- gs %>% mutate(w_pointswon = w_1stWon + w_2ndWon + l_svpt - l_1stWon - l_2ndWon,
                    l_pointswon = l_1stWon + l_2ndWon + w_svpt - w_1stWon - w_2ndWon)

@@

```{r}
remove_from_loser <- names(gs)[grep("^w|^W", names(gs))] %>%
  .[-which(. == "winner_rank")]

remove_from_winner <- names(gs)[grep("^l|^L", names(gs))] %>%
  .[-which(. %in% c("loser_rank", "league"))]

gs_l <- dplyr::select(gs, -remove_from_loser) %>%
  rename(opponent_rank = winner_rank)
gs_w <- dplyr::select(gs, -remove_from_winner)  %>%
  rename(opponent_rank = loser_rank)

names(gs_w) <- gsub("^winner_|^W|^w_", "", names(gs_w))
names(gs_l) <- gsub("^loser_|^L|^l_", "", names(gs_l))

player_gs <- bind_rows(gs_w, gs_l)

# saveRDS(player_gs, "../../data/player_gs.rda")
```
